---
title: "Analysis Report Template"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    code_folding: hide
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Load required packages
library(tidyverse)
library(knitr)
```

# Introduction

Provide an overview of your analysis, research questions, and objectives.

# Data

Describe your dataset, including:
- Data source
- Variables of interest
- Sample size
- Collection methods

```{r load-data, echo=TRUE}
# Load your data
# data <- read.csv("../data/raw/your_dataset.csv")
```

# Exploratory Data Analysis

Present descriptive statistics and initial observations.

```{r eda}
# Summary statistics
# summary(data)

# Example visualization
# ggplot(data, aes(x = variable)) +
#   geom_histogram() +
#   theme_minimal()
```

# Methods

Describe your analytical approach and statistical methods.

## Data Preprocessing

Explain any data cleaning or transformation steps.

## Statistical Analysis

Describe the statistical models or tests used.

# Results

Present your findings with tables and figures.

```{r analysis}
# Your analysis code here
```

# Discussion

Interpret your results and discuss their implications.

## Key Findings

Summarize the main results.

## Limitations

Discuss any limitations of the analysis.

# Conclusions

Provide concluding remarks and potential future directions.

# References

List any references or citations.

---

# Session Information

```{r session-info}
sessionInfo()
```
